Sustainable computational science:\\ the ReScience initiative

### 2017-07-13 draft.tex
Added references from #39

\clearpage
\section*{Introduction}
There is a replication crisis in Science. This crisis has been
highlighted in fields as diverse as medicine \citep{ioannidis:2005},
psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
behind such non-replicability are as diverse as the domains in which it occurs.
In medicine, factors such as {\em study power and bias, the
number of other studies on the same question, and importantly, the
ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}. 
In psychology, non-replicability has been blamed on spurious p-values (p-hacking),
while in the biomedical sciences \citep{iqbal:2016},
a {\em lack of access to full datasets and detailed protocols for both
clinical and non-clinical biomedical investigation} is seen as a
critical factor.
The same remarks were recently issued for chemistry \citep{coudert:2017}.
Surprisingly, the computational sciences (in the broad
sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the fact they rely on code and data rather than on experimental observations, which should make them immune to the aforementioned problems.\\

>>>>

\clearpage
\section*{Introduction}
There is a replication crisis in Science \citep{Baker:2016, Munaf:2017}. This
crisis has been highlighted in fields as diverse as medicine
\citep{ioannidis:2005}, psychology \citep{nosek:2015}, the political sciences
\citep{janz:2015}, and recently in the biomedical sciences
\citep{iqbal:2016}. The reasons behind such non-replicability are as diverse as
the domains in which it occurs.  In medicine, factors such as {\em study power
  and bias, the number of other studies on the same question, and importantly,
  the ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}.  In
psychology, non-replicability has been blamed on spurious p-values (p-hacking),
while in the biomedical sciences \citep{iqbal:2016}, a {\em lack of access to
  full datasets and detailed protocols for both clinical and non-clinical
  biomedical investigation} is seen as a critical factor.  The same remarks
were recently issued for chemistry \citep{coudert:2017}.  Surprisingly, the
computational sciences (in the broad sense) and computer sciences (in the
strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the
fact they rely on code and data rather than on experimental observations, which
should make them immune to the aforementioned problems.\\
